Kindly Bent To Free Us

### 2020-07-29 kindly/slides-icfp.tex
Start adding arrows.

@@

  \pause
  Chromium is written in C/C++!\\
  Surely these bugs don't happen in high-level typed languages \dots

@@

\begin{minted}{OCaml}
let db = Dbm.opendbm "mydb" [Dbm_rdwr] 0o666 in
Dbm.add db "hello" "world";
(* ... *)
Dbm.close db;
(* ... *)
print_string (Dbm.find db "hello") (* bug! *)
\end{minted}

@@

\begin{minted}[texcomments=true]{OCaml}
let db = Dbm.opendbm "firstnames" [Dbm_rdwr] 0o666 in
Dbm.add &!db "Radanne" "Gabriel";
(* ... *)
Dbm.close db;
(* ... *)
print_string (Dbm.find &db "Saffrich") (* \N Compile time error! *)
\end{minted}

  \TODO{Add lot's of annotation w. arrows/pointers to explain the code piece by piece}

>>>>

\tikzset{
  annot/.style={align=center,draw=black,scale=0.9,text depth=0pt,rounded corners=6pt, thick},
  onslide/.code args={<#1>#2}{\only<#1>{\pgfkeysalso{#2}}},
}
\tikzstyle{link}=[->,>=latex, rounded corners=6pt, thick]
\newcommand\tikzcoord[1]{%
  \tikz[baseline,remember picture]{\node[coordinate] (#1) {};}}

@@

  \pause
  Chromium is written in C/C++!\\
  Surely these bugs don't happen in high-level typed languages\alt<3>{ \dots right?}{.}

@@

\begin{minted}{OCaml}
let db : database = Dbm.opendbm "mydb" [Dbm_rdwr] 0o666 in
Dbm.add db "hello" "world";
(* ... *)
Dbm.close db;
(* ... *)
print_string (Dbm.find db "hello") (* bug! *)
\end{minted}

@@

\begin{minted}[texcomments=true,escapeinside=\#\#]{OCaml}
let db : data#\tikzcoord{db}#base = Dbm.opendbm "mydb" [Dbm_rdwr] 0o666 in
Dbm.add &!#\tikzcoord{borrow1}#db "hello" "world"#\tikzcoord{string}#;
(* ... *)
Dbm.close db;
(* ... *)
print_string (Dbm.find &#\tikzcoord{borrow2}#db "hello") (* \N Compile time error! *)
\end{minted}

  \begin{tikzpicture}[remember picture,overlay]
    \begin{onlyenv}<2->
      \draw[overlay,link] ($(db)+(0,1em)$) to[out=90,in=180]
      +(2,1) node[annot,anchor=west]
      {@type database : lin (* Linear kind *)@};
      \draw[overlay,link] ($(string)+(-1em,-0.2em)$) to[out=-30,in=180]
      +(1.5,-0.1) node[annot,anchor=west]
      {@type string : un (* Unrestricted kind *)@};
    \end{onlyenv}
    \begin{onlyenv}<3->
      \node[annot] at ($(borrow1)+(1.8,-0.8)$) (borrows) {Borrows!};
      \draw[overlay,link] ($(borrow1)-(0,0.2em)$) to[out=-60,in=120] (borrows) ;
      \draw[overlay,link] ($(borrow2)+(0,1em)$) to[out=120,in=-60] (borrows) ;
    \end{onlyenv}
  \end{tikzpicture}
\end{frame}
